### 2020-01-10 paper/paper.tex
introduction; discussion

@@

% typesetting words
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\expres}{\project{\acronym{EXPRES}}}
\newcommand{\name}{\project{NameOfThis}}

@@

\section*{\raggedright%
\name:
A non-parametric, hierarchical model for a laser-comb-calibrated spectrograph}

@@

\paragraph{Abstract:}
There have been many hardware improvements in polygonal-fiber-fed,
temperature-controlled, laser-frequency-comb or etalon-calibrated,
high-resolution, extreme-precision radial-velocity spectrographs.
Have the calibration methodologies improved to match?
Here are three relevant observations:
The first is that the calibration lines or spots from an etalon or
comb fill the spectral range with dense calibration points.
The second is that the spectrograph lives in a stabilized,
climate-controlled environment, in which the full optical system and
detectors will only vary within a tiny range of configurations or
settings.
The third is that---given this stability--- every calibration image
ever taken is relevant to every science exposure ever taken; there is
no reason to calibrate every exposure independently.
The calibration methodology we propose here---\name---addresses these
three problems by going non-parametric (no more polynomials!) and then
reducing dimensionality with a robust principal-component method.
We demonstrate the success of this method with data from the
\expres\ spectrograph.
We find... [results and so on].

@@

Why non-parametric?
(because density of lines given by the LFC)

Why hierarchical?
(Because stability of new instruments)

@@

\section{Discussion} \label{sec:discussion}
Generalization to etalon

@@

>>>>

% style notes
% -----------
% - use \acronym and use \eprv, \lfc, and so on.

@@

% typesetting words
\newcommand{\project}[1]{\textsl{#1}}
\newcommand{\acronym}[1]{{\small{#1}}}
\newcommand{\expres}{\project{\acronym{EXPRES}}}
\newcommand{\name}{\project{NameOfThis}}
\newcommand{\eprv}{\acronym{EPRV}}
\newcommand{\lfc}{\acronym{LFC}}

% math shih
\newcommand{\mps}{\mathrm{m\,s^{-1}}}

@@

\section*{\raggedright%
\name:
A non-parametric, hierarchical model for a precision spectrograph}

@@

\paragraph{Abstract:}
There have been many hardware improvements in polygonal-fiber-fed,
temperature-controlled, laser-frequency-comb or etalon-calibrated,
high-resolution, extreme-precision radial-velocity spectrographs.
Have the calibration methodologies improved to match?
Here are three relevant observations:
The first is that the calibration lines or spots from an etalon or
comb (or even arc lamp) fill the spectral range with dense calibration points.
The second is that the spectrograph lives in a stabilized,
climate-controlled environment, in which the full optical system and
detectors will only vary within a tiny range of configurations or
settings.
The third is that, given this stability, every calibration image
ever taken is relevant to every science exposure ever taken; there is
no reason to calibrate every exposure independently.
The calibration methodology we propose here---\name---addresses these
three problems by going non-parametric (no more polynomials!) and then
reducing dimensionality with a robust principal-component method.
We demonstrate the success of this method with data from the
\expres\ spectrograph.
We find... [results and so on].

@@

Extreme precision radial-velocity (\eprv) programs have been
outrageously successful in finding and characterizing extra-solar
planets (CITE THINGS).
These programs typically make use of spectrographs with resolutions on
the order of $10^5$, which correspond to line widths on the order of
$3000\,\mps$.
Exoplanet science happens at $3\,\mps$ precisions, and the current
instruments hope to get to $0.1\,\mps$ precisions (CITE THINGS).
This means that new spectrographs are expected to be calibrated or
stabilized to better than $10^{-4}$ of a pixel (assuming that the
spectrograph is well sampled).
And indeed, some hardware--software systems seem to be reaching these
levels (CITE THINGS).

Here we propose to simplify and improve calibration programs for
\eprv\ hardware systems with two very simple but novel ideas.
The first flows from the observation that calibration sources---which
include lamps, etalons, and laser-frequency combs (\lfc
s)---illuminate the spectrograph with dense sets of lines; almost every
location in the spectrograph image plane is surrounded by nearby,
useful calibration lines.
This recommends a calibration methodology that is
\emph{non-parametric}:
If every point in the spectrograph detector is surrounded by nearby
calibration lines, the wavelength solution can be made simply an
interpolation of the calibration data.
There is no need to choose any functional form for the wavelength
solution, such as an eighth-order polynomial.
Going non-parametric will improve calibration accuracy, because
choosing a parametric form biases the calibration, and biases it
badly when the form is inappropriate.

The second idea here flows from the observation that contemporary
\eprv\ instruments are incredibly stable.
Temperature-controlled, fiber-fed pectrographs vary only slightly over
the night or season, and only along a small number of axes in what you
might call ``calibration space''..... HOGG

@@

\section{Discussion} \label{sec:discussion}

Generalization to etalon

@@

Some ideas about self-calibration. Once you know the space in which the
spectrograph lives, every single science frame gives you information about
where you are in that space; you don't need to look at the \lfc.
